CRDS Server Documentation

### 2014-07-18 docs/server_guide/build/latex/crds_server.tex
More server_guide
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@1570 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

% Generated by Sphinx.
\def\sphinxdocclass{report}
\documentclass[letterpaper,10pt,english]{sphinxmanual}
\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{00A0}{\nobreakspace}
\usepackage{cmap}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{times}
\usepackage[Bjarne]{fncychap}
\usepackage{longtable}
\usepackage{sphinx}
\usepackage{multirow}

@@

\title{CRDS Server Documentation}
\date{July 17, 2014}
\release{1.1}
\author{STScI}
\newcommand{\sphinxlogo}{\includegraphics{stsci_logo.pdf}\par}
\renewcommand{\releasename}{Release}
\makeindex

@@

\expandafter\def\csname PYG@tok@gd\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PYG@tok@gu\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PYG@tok@gt\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\expandafter\def\csname PYG@tok@gs\endcsname{\let\PYG@bf=\textbf}
\expandafter\def\csname PYG@tok@gr\endcsname{\def\PYG@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PYG@tok@cm\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\expandafter\def\csname PYG@tok@vg\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\expandafter\def\csname PYG@tok@m\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\expandafter\def\csname PYG@tok@mh\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\expandafter\def\csname PYG@tok@cs\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}\def\PYG@bc##1{\setlength{\fboxsep}{0pt}\colorbox[rgb]{1.00,0.94,0.94}{\strut ##1}}}
\expandafter\def\csname PYG@tok@ge\endcsname{\let\PYG@it=\textit}
\expandafter\def\csname PYG@tok@vc\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\expandafter\def\csname PYG@tok@il\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\expandafter\def\csname PYG@tok@go\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.20,0.20,0.20}{##1}}}
\expandafter\def\csname PYG@tok@cp\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@gi\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PYG@tok@gh\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PYG@tok@ni\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.84,0.33,0.22}{##1}}}
\expandafter\def\csname PYG@tok@nl\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.13,0.44}{##1}}}
\expandafter\def\csname PYG@tok@nn\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
\expandafter\def\csname PYG@tok@no\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.38,0.68,0.84}{##1}}}
\expandafter\def\csname PYG@tok@na\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@nb\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@nc\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
\expandafter\def\csname PYG@tok@nd\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.33,0.33,0.33}{##1}}}
\expandafter\def\csname PYG@tok@ne\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@nf\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.49}{##1}}}
\expandafter\def\csname PYG@tok@si\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.44,0.63,0.82}{##1}}}
\expandafter\def\csname PYG@tok@s2\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@vi\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\expandafter\def\csname PYG@tok@nt\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.45}{##1}}}
\expandafter\def\csname PYG@tok@nv\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\expandafter\def\csname PYG@tok@s1\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@gp\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
\expandafter\def\csname PYG@tok@sh\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@ow\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@sx\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
\expandafter\def\csname PYG@tok@bp\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@c1\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\expandafter\def\csname PYG@tok@kc\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@c\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\expandafter\def\csname PYG@tok@mf\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\expandafter\def\csname PYG@tok@err\endcsname{\def\PYG@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PYG@tok@kd\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@ss\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.32,0.47,0.09}{##1}}}
\expandafter\def\csname PYG@tok@sr\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.14,0.33,0.53}{##1}}}
\expandafter\def\csname PYG@tok@mo\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\expandafter\def\csname PYG@tok@mi\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\expandafter\def\csname PYG@tok@kn\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@o\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PYG@tok@kr\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@s\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@kp\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@w\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PYG@tok@kt\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.56,0.13,0.00}{##1}}}
\expandafter\def\csname PYG@tok@sc\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@sb\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@k\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@se\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@sd\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}

\def\PYGZbs{\char`\\}
\def\PYGZus{\char`\_}
\def\PYGZob{\char`\{}
\def\PYGZcb{\char`\}}
\def\PYGZca{\char`\^}
\def\PYGZam{\char`\&}
\def\PYGZlt{\char`\<}
\def\PYGZgt{\char`\>}
\def\PYGZsh{\char`\#}
\def\PYGZpc{\char`\%}
\def\PYGZdl{\char`\$}
\def\PYGZhy{\char`\-}
\def\PYGZsq{\char`\'}
\def\PYGZdq{\char`\"}
\def\PYGZti{\char`\~}
% for compatibility with earlier versions
\def\PYGZat{@}
\def\PYGZlb{[}
\def\PYGZrb{]}
\makeatother

@@

\chapter{Introduction}
\label{server_guide:introduction}\label{server_guide::doc}\label{server_guide:crds-server-guide}
This guide is intended to introduce the CRDS servers for the purposes of maintenance and emergency backup for Todd.

@@

@@

\begin{Verbatim}[commandchars=\\\{\}]
\PYGZpc{} ssh \PYGZhy{}A \PYGZhy{}t \PYGZdl{}1.stsci.edu /usr/bin/sudo /bin/su \PYGZhy{} crds
\end{Verbatim}

@@

\begin{Verbatim}[commandchars=\\\{\}]
\PYGZpc{} crds\PYGZus{}server plhstcrdsv1
\PYGZsh{} crds\PYGZus{}server \PYGZlt{}VM\PYGZhy{}hostname\PYGZgt{}
\end{Verbatim}

@@

\begin{tabulary}{\linewidth}{|L|L|L|L|L|}
\hline
\textsf{\relax 
observatory
} & \textsf{\relax 
use
} & \textsf{\relax 
host/vm
} & \textsf{\relax 
direct port
} & \textsf{\relax 
url
}\\
\hline
hst
 & 
django
 & 
localhost
 & 
8000
 & 
\href{http://localhost:8000}{http://localhost:8000}
\\

hst
 & 
dev
 & 
dlhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds-dev.stsci.edu}{https://hst-crds-dev.stsci.edu}
\\

hst
 & 
test
 & 
tlhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds-test.stsci.edu}{https://hst-crds-test.stsci.edu}
\\

hst
 & 
ops
 & 
plhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds.stsci.edu}{https://hst-crds.stsci.edu}
\\

jwst
 & 
django
 & 
localhost
 & 
8000
 & 
\href{http://localhost:8000}{http://localhost:8000}
\\

jwst
 & 
dev
 & 
dljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds-dev.stsci.edu}{https://jwst-crds-dev.stsci.edu}
\\

jwst
 & 
test
 & 
tljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds-test.stsci.edu}{https://jwst-crds-test.stsci.edu}
\\

jwst
 & 
ops
 & 
pljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds.stsci.edu}{https://jwst-crds.stsci.edu}
\\
\hline\end{tabulary}

@@

See CRDS\_server/sources/site\_config.py to verify this information.

@@

\begin{tabulary}{\linewidth}{|L|L|L|}
\hline
\textsf{\relax 
mailing list
} & \textsf{\relax 
moderator
} & \textsf{\relax 
purpose
}\\
\hline
\href{mailto:crds@stsci.edu}{crds@stsci.edu}
 & 
mcmaster
 & 
comm between INS and CRDS team, also accidental use
\\

\href{mailto:crds\_team@stsci.edu}{crds\_team@stsci.edu}
 & 
mcmaster
 & 
comm within CRDS delivery team, DSB, archive, pipelines
\\

\href{mailto:crds\_datamng@stsci.edu}{crds\_datamng@stsci.edu}
 & 
mcmaster
 & 
common destination for affected datasets output
\\

\href{mailto:crds-servers@stsci.edu}{crds-servers@stsci.edu}
 & 
jmiller
 & 
little used,  new source address for affected datasets,  server details + news
\\

\href{mailto:crds\_hst\_ops\_reprocessing@stsci.edu}{crds\_hst\_ops\_reprocessing@stsci.edu}
 & 
jmiller
 & 
affected datasets output list, hst ops
\\

\href{mailto:crds\_hst\_test\_reprocessing@stsci.edu}{crds\_hst\_test\_reprocessing@stsci.edu}
 & 
jmiller
 & 
affected datasets output list, hst test
\\

\href{mailto:crds\_jwst\_ops\_reprocessing@stsci.edu}{crds\_jwst\_ops\_reprocessing@stsci.edu}
 & 
jmiller
 & 
affected datasets output list, jwst ops
\\

\href{mailto:crds\_jwst\_test\_reprocessing@stsci.edu}{crds\_jwst\_test\_reprocessing@stsci.edu}
 & 
jmiller
 & 
affected datasets output list, jwst test
\\
\hline\end{tabulary}

@@

\begin{Verbatim}[commandchars=\\\{\}]
CRDS\PYGZus{}PROJECT        jwst
CRDS\PYGZus{}USECASE        dev
CRDS\PYGZus{}SERVER         dljwstcrdsv1
CRDS                /crds/data1/dljwstcrdsv1
PATH                /crds/data1/dljwstcrdsv1/CRDS\PYGZus{}server/host   /crds/data1/dljwstcrdsv1/crds\PYGZus{}stacks/crds\PYGZus{}11/bin
CRDS\PYGZus{}STACK          /crds/data1/dljwstcrdsv1/crds\PYGZus{}stacks/crds\PYGZus{}11
CRDS\PYGZus{}AFFECTED...    jmiller@stsci.edu eisenhamer@stsci.edu
CRDS\PYGZus{}IFS            /ifs/crds/jwst/dev
CRDS\PYGZus{}FILE\PYGZus{}CACHE     /ifs/crds/jwst/dev/file\PYGZus{}cache
CRDS\PYGZus{}SERVER\PYGZus{}FILES   /ifs/crds/jwst/dev/server\PYGZus{}files
META\PYGZus{}PREFIX         /crds/data1/dljwstcrdsv1/crds\PYGZus{}stacks/crds\PYGZus{}11
\end{Verbatim}

>>>>

% Generated by Sphinx.
\def\sphinxdocclass{report}
\documentclass[letterpaper,10pt,english]{sphinxmanual}
\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{00A0}{\nobreakspace}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{times}
\usepackage[Bjarne]{fncychap}
\usepackage{longtable}
\usepackage{sphinx}
\usepackage{multirow}

\usepackage{enumitem}
\setlistdepth{15}

@@

\title{CRDS Server Documentation}
\date{July 18, 2014}
\release{1.1}
\author{STScI}
\newcommand{\sphinxlogo}{\includegraphics{stsci_logo.pdf}\par}
\renewcommand{\releasename}{Release}
\makeindex

@@

\def\PYG@tok@gd{\def\PYG@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\def\PYG@tok@gu{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\def\PYG@tok@gt{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.25,0.82}{##1}}}
\def\PYG@tok@gs{\let\PYG@bf=\textbf}
\def\PYG@tok@gr{\def\PYG@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\def\PYG@tok@cm{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\def\PYG@tok@vg{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\def\PYG@tok@m{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@mh{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@cs{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}\def\PYG@bc##1{\colorbox[rgb]{1.00,0.94,0.94}{##1}}}
\def\PYG@tok@ge{\let\PYG@it=\textit}
\def\PYG@tok@vc{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\def\PYG@tok@il{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@go{\def\PYG@tc##1{\textcolor[rgb]{0.19,0.19,0.19}{##1}}}
\def\PYG@tok@cp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@gi{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\def\PYG@tok@gh{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\def\PYG@tok@ni{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.84,0.33,0.22}{##1}}}
\def\PYG@tok@nl{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.13,0.44}{##1}}}
\def\PYG@tok@nn{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
\def\PYG@tok@no{\def\PYG@tc##1{\textcolor[rgb]{0.38,0.68,0.84}{##1}}}
\def\PYG@tok@na{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@nb{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@nc{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
\def\PYG@tok@nd{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.33,0.33,0.33}{##1}}}
\def\PYG@tok@ne{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@nf{\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.49}{##1}}}
\def\PYG@tok@si{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.44,0.63,0.82}{##1}}}
\def\PYG@tok@s2{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@vi{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\def\PYG@tok@nt{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.45}{##1}}}
\def\PYG@tok@nv{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\def\PYG@tok@s1{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@gp{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
\def\PYG@tok@sh{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@ow{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@sx{\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
\def\PYG@tok@bp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@c1{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\def\PYG@tok@kc{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@c{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\def\PYG@tok@mf{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@err{\def\PYG@bc##1{\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{##1}}}
\def\PYG@tok@kd{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@ss{\def\PYG@tc##1{\textcolor[rgb]{0.32,0.47,0.09}{##1}}}
\def\PYG@tok@sr{\def\PYG@tc##1{\textcolor[rgb]{0.14,0.33,0.53}{##1}}}
\def\PYG@tok@mo{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@mi{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@kn{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@o{\def\PYG@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\def\PYG@tok@kr{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@s{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@kp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@w{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\def\PYG@tok@kt{\def\PYG@tc##1{\textcolor[rgb]{0.56,0.13,0.00}{##1}}}
\def\PYG@tok@sc{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@sb{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@k{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@se{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@sd{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}

\def\PYGZbs{\char`\\}
\def\PYGZus{\char`\_}
\def\PYGZob{\char`\{}
\def\PYGZcb{\char`\}}
\def\PYGZca{\char`\^}
\def\PYGZsh{\char`\#}
\def\PYGZpc{\char`\%}
\def\PYGZdl{\char`\$}
\def\PYGZti{\char`\~}
% for compatibility with earlier versions
\def\PYGZat{@}
\def\PYGZlb{[}
\def\PYGZrb{]}
\makeatother

@@

\chapter{Introduction}
\label{server_guide:introduction}\label{server_guide::doc}\label{server_guide:crds-server-guide}
This guide is intended to introduce the CRDS servers for the purposes of maintenance and emergency backup for Todd.
Additional documentation about using CRDS and the servers can be located on the servers under the question mark icon
at the top right each page.

@@

\item {} 
Pey-Lian Lim:        intial JWST cloned references and rules, jwst\_gentools branch

\item {} 
Jonathan Eisenhamer  table differencing and reprocessing implications

@@

\begin{Verbatim}[commandchars=\\\{\}]
\% ssh -A -t \$1.stsci.edu /usr/bin/sudo /bin/su - crds
\end{Verbatim}

@@

\begin{Verbatim}[commandchars=\\\{\}]
\% crds\_server plhstcrdsv1
\# crds\_server \textless{}VM-hostname\textgreater{}
\end{Verbatim}

@@

\begin{tabulary}{\linewidth}{|L|L|L|L|L|}
\hline
\textbf{
observatory
} & \textbf{
use
} & \textbf{
host/vm
} & \textbf{
direct port
} & \textbf{
url
}\\\hline

hst
 & 
django
 & 
localhost
 & 
8000
 & 
\href{http://localhost:8000}{http://localhost:8000}
\\\hline

hst
 & 
dev
 & 
dlhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds-dev.stsci.edu}{https://hst-crds-dev.stsci.edu}
\\\hline

hst
 & 
test
 & 
tlhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds-test.stsci.edu}{https://hst-crds-test.stsci.edu}
\\\hline

hst
 & 
ops
 & 
plhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds.stsci.edu}{https://hst-crds.stsci.edu}
\\\hline

jwst
 & 
django
 & 
localhost
 & 
8000
 & 
\href{http://localhost:8000}{http://localhost:8000}
\\\hline

jwst
 & 
dev
 & 
dljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds-dev.stsci.edu}{https://jwst-crds-dev.stsci.edu}
\\\hline

jwst
 & 
test
 & 
tljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds-test.stsci.edu}{https://jwst-crds-test.stsci.edu}
\\\hline

jwst
 & 
ops
 & 
pljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds.stsci.edu}{https://jwst-crds.stsci.edu}
\\\hline
\end{tabulary}

@@

See CRDS\_server/sources/site\_config.py to verify server configuration.

\section{CRDS Client Configuration Scripts}
\label{server_guide:crds-client-configuration-scripts}
Configuring the client to work with various CRDS servers can be accomplished using scripts define in the CRDS client
under trunk/envs:

\begin{tabulary}{\linewidth}{|L|L|L|L|}
\hline
\textbf{
Script
} & \textbf{
CRDS\_SERVER\_URL
} & \textbf{
CRDS\_PATH
} & \textbf{
Purpose
}\\\hline

default
 & 
\href{https://crds-serverless-mode.stsci.edu}{https://crds-serverless-mode.stsci.edu}
 & 
readonly /grp/crds/cache
 & 
Default no env, serverless jwst ops
\\\hline

env-forwarded.csh
 & 
\href{https://localhost:8001}{https://localhost:8001}
 & 
\$HOME/crds\_cache\_forwarded
 & 
ssh port forwarded private server
\\\hline

env-local.csh
 & 
\href{https://localhost:8000}{https://localhost:8000}
 & 
\$HOME/crds\_cache\_local
 & 
Django development server
\\\hline

hst-crds-dev.csh
 & 
\href{https://hst-crds-dev.stsci.edu}{https://hst-crds-dev.stsci.edu}
 & 
\$HOME/crds\_cache\_dev
 & 
Connected hst dev local cache
\\\hline

hst-crds-test.csh
 & 
\href{https://hst-crds-test.stsci.edu}{https://hst-crds-test.stsci.edu}
 & 
\$HOME/crds\_cache\_test
 & 
Connected hst test local cache
\\\hline

hst-crds-ops.csh
 & 
\href{https://hst-crds.stsci.edu}{https://hst-crds.stsci.edu}
 & 
\$HOME/crds\_cache\_ops
 & 
Connected hst ops local cache
\\\hline

jwst-crds-dev.csh
 & 
\href{https://jwst-crds-dev.stsci.edu}{https://jwst-crds-dev.stsci.edu}
 & 
\$HOME/crds\_cache\_dev
 & 
Connected jwst dev local cache
\\\hline

jwst-crds-test.csh
 & 
\href{https://jwst-crds-test.stsci.edu}{https://jwst-crds-test.stsci.edu}
 & 
\$HOME/crds\_cache\_test
 & 
Connected jwst test local cache
\\\hline

jwst-crds-ops.csh
 & 
\href{https://jwst-crds.stsci.edu}{https://jwst-crds.stsci.edu}
 & 
\$HOME/crds\_cache\_ops
 & 
Connected jwst ops local cache
\\\hline

crds-readonly.csh
 & 
\href{https://crds-serverless-mode.stsci.edu}{https://crds-serverless-mode.stsci.edu}
 & 
readonly /grp/crds/cache
 & 
Disconnected, complete ops cache
\\\hline

hst-crds-readonly.csh
 & 
\href{https://hst-crds.stsci.edu}{https://hst-crds.stsci.edu}
 & 
readonly /grp/crds/hst
 & 
Connected, complete ops cache
\\\hline

jwst-crds-readonly.csh
 & 
\href{https://jwst-crds.stsci.edu}{https://jwst-crds.stsci.edu}
 & 
readonly /grp/crds/jwst
 & 
Connected, complete ops cache
\\\hline
\end{tabulary}

At present only connected clients can resolve symbolic/date-based contexts other than -operational.

Even without env settings,  many tools can guess the appropriate cache and ops server url based on files.

@@

\begin{tabulary}{\linewidth}{|L|L|L|}
\hline
\textbf{
mailing list
} & \textbf{
moderator
} & \textbf{
purpose
}\\\hline

\href{mailto:crds@stsci.edu}{crds@stsci.edu}
 & 
mcmaster
 & 
comm between INS and CRDS team, also accidental use
\\\hline

\href{mailto:crds\_team@stsci.edu}{crds\_team@stsci.edu}
 & 
mcmaster
 & 
comm within CRDS delivery team, DSB, archive, pipelines
\\\hline

\href{mailto:crds\_datamng@stsci.edu}{crds\_datamng@stsci.edu}
 & 
mcmaster
 & 
common destination for affected datasets output
\\\hline

\href{mailto:crds-servers@stsci.edu}{crds-servers@stsci.edu}
 & 
jmiller
 & 
little used,  new source address for affected datasets,  server details + news
\\\hline

\href{mailto:crds\_hst\_ops\_reprocessing@stsci.edu}{crds\_hst\_ops\_reprocessing@stsci.edu}
 & 
jmiller
 & 
affected datasets output list, hst ops
\\\hline

\href{mailto:crds\_hst\_test\_reprocessing@stsci.edu}{crds\_hst\_test\_reprocessing@stsci.edu}
 & 
jmiller
 & 
affected datasets output list, hst test
\\\hline

\href{mailto:crds\_jwst\_ops\_reprocessing@stsci.edu}{crds\_jwst\_ops\_reprocessing@stsci.edu}
 & 
jmiller
 & 
affected datasets output list, jwst ops
\\\hline

\href{mailto:crds\_jwst\_test\_reprocessing@stsci.edu}{crds\_jwst\_test\_reprocessing@stsci.edu}
 & 
jmiller
 & 
affected datasets output list, jwst test
\\\hline
\end{tabulary}

@@

\begin{Verbatim}[commandchars=\\\{\}]
CRDS\_PROJECT        jwst
CRDS\_USECASE        dev
CRDS\_SERVER         dljwstcrdsv1
CRDS                /crds/data1/dljwstcrdsv1
PATH                /crds/data1/dljwstcrdsv1/CRDS\_server/host   /crds/data1/dljwstcrdsv1/crds\_stacks/crds\_11/bin
CRDS\_STACK          /crds/data1/dljwstcrdsv1/crds\_stacks/crds\_11
CRDS\_AFFECTED...    jmiller@stsci.edu eisenhamer@stsci.edu
CRDS\_IFS            /ifs/crds/jwst/dev
CRDS\_FILE\_CACHE     /ifs/crds/jwst/dev/file\_cache
CRDS\_SERVER\_FILES   /ifs/crds/jwst/dev/server\_files
META\_PREFIX         /crds/data1/dljwstcrdsv1/crds\_stacks/crds\_11
\end{Verbatim}
